>

### 2024-09-05 docs/article.qmd
Configure line spacing in flextable when rendering to LaTeX

res_tbl_overview$overview |>
  dplyr::mutate(
    "mean_sd" = sprintf("%s (%.2f)", prettyNum(mean_claim, big.mark = ","), sd_claim),
    "median_IQR" = sprintf("%s (%.2f)", prettyNum(median_claim, big.mark = ","), IQR_claim),
    "Range" = sprintf("%s - %s", prettyNum(min_claim, big.mark = ","), prettyNum(max_claim, big.mark = ","))
  ) |>
  dplyr::select(day, mean_sd, median_IQR, Range) |>
  flextable::flextable() |>
  flextable::set_header_labels(
    day = "Day",
    mean_sd = "Mean (SD)",
    median_IQR = "Median (IQR)"
  ) |>
  flextable::add_header_row(
    values    = c("", "Number of Claims"),
    colwidths = c(1, 3),
    top       = TRUE
  ) |>
  flextable::align(align = "center", part = "all") |>
  flextable::align(j = 1, align = "left", part = "all") |>
  #flextable::font(fontname = "Times", part = "all") |>
  flextable::fontsize(size = 7, part = "all") |>
  flextable::autofit(add_w = 0, add_h = 0) |>
  flextable::line_spacing(space = 0.7, part = "all")

@@

res_recon_stat |>
  dplyr::arrange(-eigen_mean) |>
  dplyr::mutate(
    "mean_sd_eigen"     = sprintf("%.3f [%.3f]", eigen_mean, eigen_sd),
    "median_IQR_eigen"  = sprintf("%.3f [%.3f]", eigen_median, eigen_IQR),
    "mean_sd_dose"      = sprintf("%.2f [%.2f]", dose_mean, dose_sd),
    "median_IQR_dose"   = sprintf("%.2f [%.2f]", dose_median, dose_IQR),
    "mean_sd_weight"    = sprintf("%.2f [%.2f]", weight_mean, weight_sd),
    "median_IQR_weight" = sprintf("%.2f [%.2f]", weight_median, weight_IQR),
    "range_dose"        = sprintf("%.2f - %.2f", dose_min, dose_max),
    "range_weight"      = sprintf("%.2f - %.2f", weight_min, weight_max)
  ) |>
  subset(select = c(group, n_claim, mean_sd_eigen, mean_sd_dose, median_IQR_dose, mean_sd_weight)) |>
  flextable::flextable() |>
  flextable::set_header_labels(
    group            = "",
    n_claim          = "Claim",
    mean_sd_eigen    = "Mean [SD]",
    mean_sd_dose     = "Mean [SD]",
    median_IQR_dose  = "Median [IQR]",
    mean_sd_weight   = "Mean [SD]"
  ) |>
  flextable::add_header_row(
    values    = c("", "Importance", "Defined Daily Dose", "Weight"),
    colwidths = c(2, 1, 2, 1),
    top       = TRUE
  ) |>
  flextable::align(align = "center", part = "all") |>
  flextable::align(j = 1, align = "left", part = "body") |>
  #flextable::font(fontname = "Times", part = "all") |>
  flextable::fontsize(size = 7, part = "all") |>
  flextable::autofit(add_w = 0, add_h = 0) |>
  flextable::line_spacing(space = 0.7, part = "all")

>>>>

res_tbl_overview$overview |>
  dplyr::mutate(
    "mean_sd" = sprintf("%s (%.2f)", prettyNum(mean_claim, big.mark = ","), sd_claim),
    "median_IQR" = sprintf("%s (%.2f)", prettyNum(median_claim, big.mark = ","), IQR_claim),
    "Range" = sprintf("%s - %s", prettyNum(min_claim, big.mark = ","), prettyNum(max_claim, big.mark = ","))
  ) |>
  dplyr::select(day, mean_sd, median_IQR, Range) |>
  flextable::flextable() |>
  flextable::set_header_labels(
    day = "Day",
    mean_sd = "Mean (SD)",
    median_IQR = "Median (IQR)"
  ) |>
  flextable::add_header_row(
    values    = c("", "Number of Claims"),
    colwidths = c(1, 3),
    top       = TRUE
  ) |>
  flextable::align(align = "center", part = "all") |>
  flextable::align(j = 1, align = "left", part = "all") |>
  #flextable::font(fontname = "Times", part = "all") |>
  flextable::fontsize(size = 7, part = "all") |>
  flextable::autofit(add_w = 0, add_h = 0) |>
  flextable::set_table_properties(opts_pdf = list("arraystretch" = 1, "tabcolsep" = 0))

@@

res_recon_stat |>
  dplyr::arrange(-eigen_mean) |>
  dplyr::mutate(
    "mean_sd_eigen"     = sprintf("%.3f [%.3f]", eigen_mean, eigen_sd),
    "median_IQR_eigen"  = sprintf("%.3f [%.3f]", eigen_median, eigen_IQR),
    "mean_sd_dose"      = sprintf("%.2f [%.2f]", dose_mean, dose_sd),
    "median_IQR_dose"   = sprintf("%.2f [%.2f]", dose_median, dose_IQR),
    "mean_sd_weight"    = sprintf("%.2f [%.2f]", weight_mean, weight_sd),
    "median_IQR_weight" = sprintf("%.2f [%.2f]", weight_median, weight_IQR),
    "range_dose"        = sprintf("%.2f - %.2f", dose_min, dose_max),
    "range_weight"      = sprintf("%.2f - %.2f", weight_min, weight_max)
  ) |>
  subset(select = c(group, n_claim, mean_sd_eigen, mean_sd_dose, median_IQR_dose, mean_sd_weight)) |>
  flextable::flextable() |>
  flextable::set_header_labels(
    group            = "",
    n_claim          = "Claim",
    mean_sd_eigen    = "Mean [SD]",
    mean_sd_dose     = "Mean [SD]",
    median_IQR_dose  = "Median [IQR]",
    mean_sd_weight   = "Mean [SD]"
  ) |>
  flextable::add_header_row(
    values    = c("", "Importance", "Defined Daily Dose", "Weight"),
    colwidths = c(2, 1, 2, 1),
    top       = TRUE
  ) |>
  flextable::align(align = "center", part = "all") |>
  flextable::align(j = 1, align = "left", part = "body") |>
  #flextable::font(fontname = "Times", part = "all") |>
  flextable::fontsize(size = 7, part = "all") |>
  flextable::autofit(add_w = 0, add_h = 0) |>
  flextable::set_table_properties(opts_pdf = list("arraystretch" = 1, "tabcolsep" = 0))
